Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-26 paper.qmd
Added initial work to replace the S-curve structure with another clustering structure

```{r}
#| label: read-two-curvilinear-clust-nldr
# Read a variety of different NLDR representations of two_curvilinear_clust
# and plot them on same aspect ratio
tsne_two_curvilinear_clust <- read_rds("data/two_nonlinear_clusters/two_nonlinear_clusters_tsne_perplexity_30.rds")

@@

umap_two_curvilinear_clust <- read_rds("data/two_nonlinear_clusters/two_nonlinear_clusters_umap_n-neigbors_15_min-dist_0.1.rds")

@@

phate_two_curvilinear_clust <- read_rds("data/two_nonlinear_clusters/two_nonlinear_clusters_phate_knn_5.rds")

@@

trimap_two_curvilinear_clust <- read_rds("data/two_nonlinear_clusters/two_nonlinear_clusters_trimap_n-inliers_12_n-outliers_4_n-random_3.rds")

@@

pacmap_two_curvilinear_clust <- read_rds("data/two_nonlinear_clusters/two_nonlinear_clusters_pacmap_n-neighbors_10_init_random_MN-ratio_0.5_FP-ratio_2.rds")

@@

error_two_curvilinear_clust_umap <- read_rds("data/two_nonlinear_clusters/error_two_nonlinear_clusters_umap.rds")
error_two_curvilinear_clust_tsne <- read_rds("data/two_nonlinear_clusters/error_two_nonlinear_clusters_tsne.rds")
error_two_curvilinear_clust_phate <- read_rds("data/two_nonlinear_clusters/error_two_nonlinear_clusters_phate.rds")
error_two_curvilinear_clust_trimap <- read_rds("data/two_nonlinear_clusters/error_two_nonlinear_clusters_trimap.rds")
error_two_curvilinear_clust_pacmap <- read_rds("data/two_nonlinear_clusters/error_two_nonlinear_clusters_pacmap.rds")

>>>>

```{r}
#| label: read-two-curvilinear-clust-nldr
# Read a variety of different NLDR representations of two_curvilinear_clust
# and plot them on same aspect ratio
tsne_two_curvilinear_clust <- read_rds("data/two_curvy_clust/two_curvy_clust_tsne_perplexity_30.rds")

@@

umap_two_curvilinear_clust <- read_rds("data/two_curvy_clust/two_curvy_clust_umap_n-neigbors_15_min-dist_0.1.rds")

@@

phate_two_curvilinear_clust <- read_rds("data/two_curvy_clust/two_curvy_clust_phate_knn_5.rds")

@@

trimap_two_curvilinear_clust <- read_rds("data/two_curvy_clust/two_curvy_clust_trimap_n-inliers_12_n-outliers_4_n-random_3.rds")

@@

pacmap_two_curvilinear_clust <- read_rds("data/two_curvy_clust/two_curvy_clust_pacmap_n-neighbors_10_init_random_MN-ratio_0.5_FP-ratio_2.rds")

@@

error_two_curvilinear_clust_umap <- read_rds("data/two_curvy_clust/error_two_curvy_clust_umap.rds")
error_two_curvilinear_clust_tsne <- read_rds("data/two_curvy_clust/error_two_curvy_clust_tsne.rds")
error_two_curvilinear_clust_phate <- read_rds("data/two_curvy_clust/error_two_curvy_clust_phate.rds")
error_two_curvilinear_clust_trimap <- read_rds("data/two_curvy_clust/error_two_curvy_clust_trimap.rds")
error_two_curvilinear_clust_pacmap <- read_rds("data/two_curvy_clust/error_two_curvy_clust_pacmap.rds")
